Contention Management for 5G

### 2017-01-31 article/article.tex
modele clean

\section{Model, Problems}

@@

      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$. Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$. \todo{Est-ce qu'on doit ajouter que le routage est cohérent ?}

   \subsection{Slotted time Model}
      Consider now a positive integer $P$ called the {\bf period}. A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$
      of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of $\cal C$. In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ slots. 
      The number $m_i$ represents the number of the first slot used by the route $r_i \in {\cal R}_{\cal C}$ at its source in a period.
      We define the first time slot at which a message reaches any vertex $v$ in this route by $$t(v,r_i) = m_i+\lambda(v,r_i) \mod P.$$

      A message usually cannot be transported in a single time slot. We denote by $\tau$ the number 
      of slots necessary to transmit a message. %remarque sur le fait qu'un message est porté par des temps consécutifs ?
      Let us call $[t(v,r_i)]$ the index of the time slots used by a route $r_i$ at a vertex $v$ in a period $P$. Those values are forming a consecutive set of values starting at $t(v,r_i)$ and ending at $t(v,r_i) + \tau \mod P$. A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R}_{\cal C}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

   \todo{Mettre une phrase ou deux pour faire le lien avec le problème concret, plus facile  faire une fois l'intro écrite}
      The main theoretical problem we have to deal with in this context is the following.\\

@@

      We deal in next section with the complexity of the Problem PRA.\\
% 
%       \begin{figure}[H]
%       \label{could-ran}
%       \begin{center}
%       % \begin{tabular}{cc}
%       \includegraphics[scale=0.5]{Total-latence.pdf}
%       \caption{Complete process for a leaf in $L$.}
%       \end{center}
%       \end{figure}
%       %\end{tabular}\newline

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $L$.
      We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which defines two disjoint assignments ${\cal C}_1 = \{(l,\rho(l))\}_{l \in L}$ and ${\cal C}_2 = \{(s,\rho^{-1}(s))\}_{s \in S}$. Let ${\cal M} = (m_1,\dots, m_n)$ and ${\cal W} = (w_1,\dots, w_n)$ be two $P$-periodic affectations, of respectively ${\cal R}_{{\cal C}_1}$ and ${\cal R}_{{\cal C}_2}$.

      The process realized periodically (i.e. initiated in each window of size $P$) for each leaf $l \in L$ is the following one (see Figure \ref{cloud-ran}). First, a message of $\tau$ slots is sent from $l$ to $\rho(l)$ on ${\cal R}(l,\rho(l))$ at slot $m_l$ in the current window. After receiving this message, $\rho(l)$ computes it during a time equal to $\theta$ slots.\todo{Je suis contre
      le theta dans le modèle, car il ne set à rien. On peut dire par contre dans le blabla autour du modèle qu'on simule le temps de calcul par des arêtes plus longues}

      Then, a message of $\tau$ slots containing the computed result is sent back from $\rho(l)$ to $l$ on ${\cal R}(\rho(l),l)$, after waiting for $w_l$ slots. 
      %at the first occurrence of  step $m_{\overline l}$ in a window (i.e., in the current window at the end of computation or the next one). We denote by $\omega(l)$ the {\bf waiting time} of $l$, i.e.,  the number of slots between the end of the computation time in $\rho(l)$ and the first occurrence of  step $m_{\overline l}$ in a window. 
      Thus, the whole proccess time for $l$ is equal to
      $$
      PT(l)=\lambda({\cal R}(l,\rho(l)))+\theta+w_l+\lambda({\cal R}(\rho(l),l)).
      $$

      \todo{Il manque le fait qu'il n'y a pas de collisions ni à l'aller ni au retour.}
% 	
%       Let us denote by ${\cal C}_{\rho}$ the set of couples $<l,\rho(l)>$ and $<\rho(l),l>$, for any $l \in L$. Consider a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$. 
    The {\bf maximum process time} of $({\cal M},{\cal W})$ is defined by $MT(({\cal M},{\cal W}))=\max\limits_{l \in L} PT(l)$. The problem we want to solve, is the following.

@@

      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ of a set $S$ into a set $L$ in $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.

      \noindent {\bf Question:} does there exist a pair of $({\cal M},{\cal W})$ $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?

@@

\section{PRA Solving}

  \subsection{NP-Hardness}

>>>>

\section{Model}

@@

      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$. Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$. \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}

   \subsection{Slotted time Model}
      Consider now a positive integer $P$ called the {\bf period}. In our problem the messages we send in the network will be periodic of period $P$ and thus we consider slices of time of $P$ discrete slots. Assume we send a message at the source of the route $r$,
      at the time slot $m$ in the first period, then a message will be sent at time $m$ at each new period. We define the first time slot at which a message reaches a vertex $v$ in this route by $t(v,r) = m + \lambda(v,r) \mod P$.

      A message usually cannot be transported in a single time slot. We denote by $\tau$ the number 
      of consecutive slots necessary to transmit a message. Let us call $[t(v,r)]$ the set of time slots used by $r$ at a vertex $v$ in a period $P$, that is $[t(v,r)] = \{t(v,r) + i \mod P \mid 0 \leq i \leq \tau \}$.

      A {\bf $P$-periodic affectation} of $\cal R_{\cal C}$ consists in a set  ${\cal M}=(m_0, \ldots ,m_{c-1})$ of $c$ integers that we call {\bf offsets}, with $c$ the cardinal of the assignment $\cal C$. The number $m_i$ represents the index of the first slot used in a period  by the route $r_i \in {\cal R}_{\cal C}$ at its source.
      A $P$-periodic affectation must have no {\bf collision} between two routes in ${\cal R}_{\cal C}$, that is $\forall (r_i, r_j) \in {\cal R}_{\cal C}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_i)] \cap [t(u,r_j)] = \emptyset .$$

@@

      The main theoretical problem we have to deal with in this context is the following.\\

@@

      We will prove in Sec.~\ref{sec:complexity} that the Problem PRA is $\NP$-complete, even in restricted settings.
      In fact, even approximating the smallest value of $P$ for which there is a $P$-periodic assignment is hard.\\
% 
%       \begin{figure}[H]
%       \label{could-ran}
%       \begin{center}
%       % \begin{tabular}{cc}
%       \includegraphics[scale=0.5]{Total-latence.pdf}
%       \caption{Complete process for a leaf in $L$.}
%       \end{center}
%       \end{figure}
%       %\end{tabular}\newline

      In the context of cloud-RAN applications, we consider here the digraph $G=(V,A)$ modeling the target network 
      and two disjoint subsets of vertices $S$ and $L$, where $S$ is the set of BBU and $L$ is the set of RRH. 
      We denote by $n$ the size of $S$ and $L$. We are given a period $P$, a routing function ${\cal R}$ and a bijection $\rho:L\rightarrow S$ which assigns a BBU to each RRH. Let ${\cal C}_{\rho} = \{(l,\rho(l))\}_{l \in L} \cup \{(s,\rho^{-1}(s))\}_{s \in S}$. Let consider a $P$-periodic affectation of ${\cal C}_{\rho}$ which associates $m_l$ to 
      $(l,\rho(l))$ and $m_{\rho(l)}$ to $(\rho(l),l)$.

      This affectation represents the following process: first a message is sent in $l$, through the route $r_l$, at time $m_l$.
      This message is received by $\rho(l)$ at time $t(\rho(l),r_l)$. It is then sent back to $l$ at time $\bar{m_l}$,
      which is in the same period if $m_{\rho(l)} > t(\rho(l),r_l)$ otherwise it is in the next. The time between the arrival of
      the message and the time it is sent back is called the \textbf{waiting time} and is defined by $w_l = m_{\rho(l)} - t(\rho(l),r_l)$ if $m_{\rho(l)} > t(\rho(l),r_l)$ and $w_l = m_{\rho(l)} + P - t(\rho(l),r_l)$ otherwise.
      When a BBU receives a message, it must compute the answer before sending it back to the BBU. This time is taken into account
      in the last arc leading to the BBU and thus we need not to consider it explicitely in our model.

      Thus, the whole proccess time for a vertex $l$ is equal to
      $$
      PT(l)=\lambda(r_l)+ w_l+\lambda(r_{\rho(l)}).
      $$

    The {\bf maximum process time} of the $P$-periodic affectation ${\cal M} $ is defined by $MT({\cal M})=\max\limits_{l \in L} PT(l)$. The problem we want to solve is the following.

@@

      \noindent {\bf Input:}  a digraph $G$, a matching $\rho$ from $L$ to $S$ two disjoint set of vertices of $G$, a routing function $\cal R$, a period $P$, an integer $T_{max}$.

      \noindent {\bf Question:} does there exist a $P$-periodic affectation ${\cal M}$ of ${\cal C}_{\rho}$ in $(G,{\cal R})$ such that $MT({\cal M}) \leq T_{max}$?

@@

\section{Solving PRA}
  \label{sec:complexity}
  \subsection{NP-Hardness}
